Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
I think now that there is the explicit link to the source code of the benchmarks, this XXX can go
fix another XXX
I decided to ignore this comment, because that is dealt with by tracing itself, not by the optimization that the paper is about

XXX [fijal] I would say that the other goal of the JIT in case of dynamic
languages is to compile only a common scenario and leave a guard (instead
of proving that something will never ever happen)

@@

This problem is solved by making it possible to the interpreter author
to add some hints into the source code to declare instances of one
class as frame objects needing special treatment. The JIT will then
fill these objects only lazily when they are actually accessed (\eg
because a debugger is used) using values from JIT-emitted code runtime
locations (typically the CPU stack). Therefore in the common case,
nothing is stored into the frame objects, making the problem of too
much escaping go away. This special handling of frame objects is a common approach in VM implementations
\cite{miranda_context_1999}. The only novelty in our approach lays in
its generality: all the delicate support code for this is generated, as opposed to
most other JITs, which are just specifically written for one particular
language.

XXX one of the JS tracing JITs does this as well

@@

XXX [fijal] note that some of those have cpython-specific hacks removed or
old versions used (nbody mostly I think).

>>>>

@@

This problem is solved by making it possible to the interpreter author
to add some hints into the source code to declare instances of one
class as frame objects needing special treatment. The JIT will then
fill these objects only lazily when they are actually accessed (\eg
because a debugger is used) using values from JIT-emitted code runtime
locations (typically the CPU stack). Therefore in the common case,
nothing is stored into the frame objects, making the problem of too
much escaping go away. This special handling of frame objects is a common approach in VM implementations
\cite{miranda_context_1999,andreas_gal_trace-based_2009}. The only novelty in our approach lays in
its generality: all the delicate support code for this is generated, as opposed to
most other JITs, which are just specifically written for one particular
language.

@@
